---
title: "Paid Tickets for BVB"
author: "Arin Mahapatra"
output: html_document
date: "2024-10-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, error = TRUE)
libraries <- c("ggplot2", "dplyr", "tidyr", "readr", "tidyverse", "stringr")
lapply(libraries, library, character.only = TRUE)
```
## Product for Venmo Payments - ALL PEOPLE PAID through VENMO

Here are the contents of reading the two csv files and checking if their outputs match for the payment transactions that were made. These individuals have a TRUE next to their name, this INDICATES that they have paid their dues for the BVB and should receive a ticket confirmation.

```{r}
venmo_tickets <- read_csv("CSV/venmo_payments.csv")
orders_final <- read_csv("CSV/orders_info.csv")

venmo_tickets <- venmo_tickets %>%
  select(Datetime, From, "Amount (total)") %>% 
  mutate(FullName = From) %>% 
  slice(8:n())

orders_final <- orders_final %>%
  mutate(FullName = paste(`First Name`, `Last Name`)) %>% 
  filter(tolower(Platform) == "venmo") %>% 
  select("First Name", "Last Name", "Email", "Platform", "Local Emergency Contact - Full Name (preferably someone who is also attending BVB)", "Local Emergency Contact - Phone Number") %>% 
  mutate(FullName = paste(`First Name`, `Last Name`))

venmo_final <- venmo_tickets %>%
  left_join(orders_final, by = "FullName") %>%
  select(-`From`, -`First Name`, -`Last Name`, -`From`) %>% 
  mutate(Paid = if_else(!is.na(FullName), TRUE, FALSE)) %>% 
  drop_na()

print(venmo_final, n = Inf) # works perfectly (proper formatting included)
fullnames_list <- venmo_final %>% pull(FullName)
print(fullnames_list)

write.csv(venmo_final, "~/Desktop/ISA_BVB/venmo_list.csv", row.names = FALSE) # print into csv files
```

## Product for Zelle Payments - ALL PEOPLE PAID through ZELLE

Here are the contents of reading the two csv files and checking if their outputs match for the payment transactions that were made. These individuals have a TRUE next to their name, this INDICATES that they have paid their dues for BVB and should receive a ticket confirmation.
```{r}
orders_final <- read_csv("CSV/orders_info.csv")
zelle_list <- read_csv("CSV/zelle_list.csv")

zelle_tickets <- zelle_list %>%
  mutate(Date = as.Date(`Posted Date`, format = "%m/%d/%Y")) %>%  # Convert to Date type
  filter(Date >= as.Date("2024-09-21")) %>% 
  select(-`AccountNumber`, -`AccountType`, -`Check Number`, -`Category`, -`Note`, -`...10`, -`Date`) %>% 
  mutate(FullName = str_extract(Description, "(?<=Zelle\\s)[A-Za-z]+(?:\\s[A-Za-z]+)?")) %>%
  select(everything(), FullName) %>% 
  filter(Amount == "$25.00") %>% 
  mutate(FullName_lower = tolower(FullName)) %>% 
  mutate(FirstNamePart = str_extract(FullName, "^[^ ]+")) %>% 
  mutate(FirstNamePart = tolower(FirstNamePart))

orders_final <- orders_final %>%
  mutate(FullName = paste(`First Name`, `Last Name`)) %>% 
  filter(Platform %in% c("zelle", "Zelle")) %>% 
  mutate(FullName_lower = tolower(FullName)) %>% 
  mutate(FirstNamePart = str_extract(FullName, "^[^ ]+")) %>% 
  mutate(FirstNamePart = tolower(FirstNamePart))

zelle_final <- zelle_tickets %>%
  left_join(orders_final, by = "FirstNamePart", suffix = c("", ".order")) %>% 
  drop_na()

fullnames_list <- zelle_final %>% 
  pull(FullName) %>% 
  unique(fullnames_list)
print(fullnames_list)

write.csv(zelle_final, "~/Desktop/ISA_BVB/zelle_list.csv", row.names = FALSE)
```